%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Joel}{Adams}
\position{Computer Science{\enskip\cdotp\enskip}Artificial Intelligence}
\address{10 Beech Road, Bristol, BS78RP}

\mobile{07729430577}
\email{joelucadams@gmail.com}
\homepage{www.joeladams.dev}
\github{JoelLucaAdams}
\linkedin{joellucaadams}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Aberystwyth University Recruitment Team}
  {Penglais\\ Aberystwyth\\ SY23 3FL}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Graduate Trainee – IT Networking}
% How the letter is opened
\letteropening{\\Dear Team,}
% How the letter is closed
\letterclosing{Best regards and hope to hear from you soon,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Joel Adams~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I'm a third-year student studying for a BSc in Computer Science and Artificial Intelligence at Aberystwyth University. Concurrent to my studies I have created the Computer Science department's Discord server for which I am also an administrator. The server has over 800 members including lecturers, alumni, staff and students. I developed this community of people, which previously did not exist, and is now an essential part of the department's online presence. This server acts as a central hub for announcements from the department and as place for people to discuss a multitude of topics ranging from coding to cooking. In addition, I created a small sub community of this server where I collaborate with other students to develop Discord bots. I have spent the last three years working as a paid Demonstrator for the department of computer science, a student representative and a Computer Science Advisor, a role that is usually only given to Masters’ students.

In my free time I create Discord bots in Python, teach myself to write websites using Node.js and React, self-host websites and other services that I run off a Raspberry Pi.

Working for Oracle would provide valuable experience in my first steps into the industry as well as giving me the opportunity to gain a deeper understanding of APIs and cloud infrastructure which I use daily when working with Discord's API or Google Cloud Computing's services. 

I am an enthusiastic, self-motivated and innovative person and am looking for my first graduate job. I enjoy public speaking and working as a team leader. As an added bonus, I also speak fluent Italian as I was born in Italy to British parents and lived there until 2018. 


\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
