%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Joel}{Adams}
\position{Computer Science{\enskip\cdotp\enskip}Artificial Intelligence}
\address{10 Beech Road, Bristol, BS78RP}

\mobile{07729430577}
\email{joelucadams@gmail.com}
\homepage{joeladams.dev}
\github{JoelLucaAdams}
\linkedin{joellucaadams}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Apple Recruitment Team}
  {UK}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Apple Cloud Services - Site Reliability Engineer (SRE)}
% How the letter is opened
\letteropening{\\Dear Team,}
% How the letter is closed
\letterclosing{Best regards and hope to hear from you soon,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Joel Adams~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I'm a third-year student studying for a BSc in Computer Science and Artificial Intelligence at Aberystwyth University. Concurrent to my studies I have created the Computer Science department's Discord server for which I am also an administrator. The server has over 800 members including lecturers, alumni, staff and students. I developed this community of people, which previously did not exist, and is now an essential part of the department's online presence. This server acts as a central hub for announcements from the department and a place for people to discuss a multitude of topics ranging from coding to cooking. In addition, I created a small sub-community of this server where I collaborate with other students to develop Discord bots. I have spent the last three years working as a paid Demonstrator for the department of computer science, a student representative and a Computer Science Advisor, a role that is usually only given to Masters’ students.

In my free time, I create Discord bots in Python, teach myself to write websites using NodeJS, self-host websites, APIs and other services that I run off a Raspberry Pi. My online portfolio can be found here https://www.joeladams.dev/ on this NodeJS website along with my API https://api.joeladams.dev/ that consists of many endpoints such as the github API \\https://api.joeladams.dev/github?user=JoelLucaAdams and getting information on the Raspberry Pi and it's respective services https://api.joeladams.dev/forest. I am very familiar with Windows 10 as it has been my main OS that I have used since release, however, I am also very familiar with macOS and Linux.
  
Over the summer of 2020, I co-developed a Discord bot for the department of Computer Science to act as a service that helps with demonstrating. The department then hired me to continue to maintain the service for the staff and students, performing updates and helping the staff set up the service themselves. There were times where the service would fail in the middle of the day and I would work very well under pressure to fix the bugs that it produced and bring it back online.
  
I work well under pressure and in a team environment due to the group project that I completed in my second year to develop a Java-based translation app for English to Welsh. 

I am an enthusiastic, self-motivated and innovative person and am looking for my first graduate job. I enjoy public speaking and working as a team leader. As a bonus, I also speak fluent Italian as I was born in Italy to British parents and lived there until 2018. 


\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
