%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {ABERYSTWYTH UNIVERSITY} % Institution
    {Computer Science and Artificial Intelligence, BSc - First Class Honours} % Degree
    {Wales, UK} % Location
    {Aug. 2018 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Relevant modules}:}\\
        \begin{cvitems}
          %\item {Introduction to Object Orientated Programming OOP (Java, 1st year)}
          \item {Computational Thinking (Python, 1st year)}
          \item {Problems and Solutions (Algorithm run-time, 1st year)}
          \item {Program Design, Data Structures and Algorithms (Java, 2nd year)}
          \item {Software Engineering (Group leader of group project, 2nd year)}
          \item {Artificial Intelligence (Python, 3rd year)}
          \item {Agile Development and testing (TravisCI and Jenkins, 3rd year)}\\
        \end{cvitems}
        \item {\textbf{Major project}: AberLink connects CS students' uni accounts to their discord accounts through a website. This project also includes a front end discord bot for marking attendance in practicals and verifying discord accounts. Built webpages using HTML5 and JavaScript along with Django (Python) for the back-end web-server. The Discord bot is made using Python.}
      \end{cvitems}
    }
    
  \cventry
    {THE NEW SCHOOL} % Institution
    {A-levels} % Degree
    {Rome, Italy} % Location
    {Aug. 2016 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Achieved a BBC in Italian, Maths and Physics respectively}
      \end{cvitems}
    }
    
    \cventry
    {THE NEW SCHOOL} % Institution
    {IGCSEs} % Degree
    {Rome, Italy} % Location
    {Aug. 2014 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {English, Maths, Physics, Chemistry, Biology, History, Italian, French}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
