%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {ABERYSTWYTH UNIVERSITY} % Job title
    {Computer Science Advisor} % Organization
    {Wales, UK} % Location
    {Aug. 2020 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working as a Computer Science Advisor helping students in all years with any issues they are having related to computer science.}
        \item {Advising students on a variety of topics including; Java, Python, HTML, Javascript, PHP, understanding algorithm runtime, C and C++.}
        \item {This role is normally associated with postgrad students so being offered the position as an undergrad is rare.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ABERYSTWYTH UNIVERSITY} % Organization
    {Demonstrator} % Job title
    {Wales, UK} % Location
    {Aug. 2019 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helping first and second-year students during practicals when they are stuck on problems or need help debugging their code.}
        \item {Teaching students concepts or helping them with understanding a piece of code.}
        \item {Coaching primarily for modules using; Java, Python and C and C++ helping to greatly increase my knowledge of these modules.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ABERYSTWYTH UNIVERSITY} % Organization
    {Discord Bot Developer} % Job title
    {Wales, UK} % Location
    {Aug. 2020 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-developed and currently maintaining a system for managing 800 students during the online practicals in the department.}
        \item {Built up a simple queue system that would be dynamically created and destroyed in each Discord server.}
        \item {Approached by the university and paid to continue to develop and maintain the project.}
        \item {The bots repository can be found here along with the open source code \url{https://github.com/AberDiscordBotsTeam}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ABERYSTWYTH UNIVERSITY} % Organization
    {Academic Representative (volunteering)} % Job title
    {Wales, UK} % Location
    {Aug. 2018 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Active voice of the students providing feedback to the Computer Science department and to the lecturers directly.}
        \item {I have been voted in for this role during first, second and third year.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {THE ROYAL PIER} % Organization
    {Nightclub photographer} % Job title
    {Aberystwyth, Wales, UK} % Location
    {Aug. 2019 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working as a photographer for the nightclub from 01:00-03:00 am every other night during the week.}
        \item {Responsible for taking on average 400 pictures per session and editing them in time for the 12:00 pm release the next day on the Facebook page.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {ABERYSTWYTH UNIVERSITY (DISCORD)} % Organization
    {Comp Sci Community Hub Administrator (volunteering)} % Job title
    {N/A} % Location
    {Aug. 2019 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-founder of the Comp Sci Community Hub and the main Administrator / Moderator providing the Computer Science department of Aberystwyth University with a discord server to serve as a social environment.}
        \item {Responsible for maintaining a semi-official server under my own set of guidelines.}
        \item {Currently boasting over 800 members including lecturers and alumni.}
        \item {This server and it's success lead to the lecturers creating their own Discord servers for modules based off of a template I created.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  % \cventry
  %   {UNIVERSITY OF BRISTOL} % Organization
  %   {Research Assistant} % Job title
  %   {Bristol, UK} % Location
  %   {Jun. 2019 - Aug. 2019 \& Jun. 2020 - Aug. 2020} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Transcribed recordings of children from 1999 - 2000 to be used as research in speech therapy.}
  %       \item {Drastically increased my typing skills.}
  %     \end{cvitems}
  %   }
    
%---------------------------------------------------------
  % \cventry
  %   {FREELANCE} % Affiliation/role
  %   {Photographer} % Organization/group
  %   {Aberystwyth, Wales \& Bristol, UK} % Location
  %   {Aug. 2018 - PRESENT} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {Working as a freelance photographer at university for the Students Union and the local clubs\slash  societies.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {FREELANCE} % Affiliation/role
    {English/Italian mentor in Computer Science} % Organization/group
    {Rome, Italy} % Location
    {Jun. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Working as a freelance teacher of computer science during the summer holidays teaching kids how to code and program Arduinos.}
        \item {Taught concepts in both Italian and English to help strengthen their understanding of English vocabulary.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
