%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {N/A} % Affiliation/role
    {Discord bot developer} % Organization/group
    {Aberystwyth, Wales, UK} % Location
    {Aug. 2020 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {During my free time I have written several Discord bots which have been inspired by the Computer Science's Community Discord Hub.}
        \item {\textbf{The bots}:}\\
        \begin{cvitems}
          \item {\textbf{StressBot} - A bot that allows users to enter their stress level as a percentage (-99\%-9999\%) and stores information in a JSON file.}
          \item {\textbf{MorningBot} - Responds to the message 'morning' in Discord with a location in the world where it is currently morning despite the current time (works in over 10 languages!).}
          \item {\textbf{ManPageBot} - allows for the user to request a linux man page for a specific command using pythons module for querying the command line. e.g. !man ls}\\
        \end{cvitems}
        \item {Developed in Python and running in a Google Cloud Instance (GCP).}
        \item {They can all be found on my GitHub page and are open source.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {STUDENT'S UNION} % Affiliation/role
    {President of the Aberystwyth Photography society} % Organization/group
    {Aberystwyth, Wales, UK} % Location
    {Aug. 2018 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Co-founder of the society.}
        \item {Responsible for building up the foundations and establishing the Photography Society at Aberystwyth University.}
        \item {Created and lead many workshops helping student to learn about their cameras.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {TOASTMASTERS ITALIA, THE NEW SCHOOL ROME} % Affiliation/role
    {Toastmasters Public Speaking course} % Organization/group
    {Rome, Italy} % Location
    {Aug. 2017 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Learnt about public speaking and delivering presentations to other students.}
        \item {Came second in the final competition involving improvisational public speaking.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
